---
title: "Temperature-Induced Yield Impacts and Geographic Shifts in US Alfalfa Production"
date: "`r format(Sys.Date(), '%B %Y')`"
output:
  word_document:
    reference_docx: reference.docx
    toc: false
    number_sections: false
    fig_caption: true
  html_document:
    toc: false
    number_sections: false
    df_print: kable
bibliography: references.bib
link-citations: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 7.5, fig.height = 4.5, dpi = 150)
# Pre-calculated article values (no hard-coded results). Regenerate with
# scripts/301_article_objects.R (via scripts/run_article.R). Inline references use
# objs$... throughout the section children. Figures are pre-rendered into
# ../output/exhibits/ by scripts/100_WarmingImpactsAlfalfa_exhibits.R.
objs <- jsonlite::fromJSON("article_objects.json")
```

Francis Tsiboe\*, Program Leader, Agricultural Risk Policy Center, North Dakota State University

Hannah Shear, Assistant Professor, Department of Agricultural Economics, Oklahoma State University

Walker Davis, Graduate Student, Department of Agricultural Economics, Oklahoma State University

Jesse Tack, Professor, Department of Agricultural Economics, Kansas State University

Jisang Yu, Associate Professor, Department of Food and Resource Economics, Korea University

\* Corresponding author: ftsiboe@hotmail.com

```{r abstract, child = "sections/00_abstract.Rmd"}
```

```{r introduction, child = "sections/01_introduction.Rmd"}
```

```{r data, child = "sections/02_data.Rmd"}
```

```{r methods, child = "sections/03_methods.Rmd"}
```

```{r results, child = "sections/04_results.Rmd"}
```

```{r discussion, child = "sections/05_discussion.Rmd"}
```

```{r conclusion, child = "sections/08_conclusion.Rmd"}
```

# References

<div id="refs"></div>

```{r tables-and-figures, child = "sections/98_tables_and_figures.Rmd"}
```
